Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-29 article.tex
There is no empirical evidence that hydrophobic residues bind more often, lund2004 only uses hydrophobic residues for classification

Any human's immune system detects only a fraction of all possible
polypeptide fragments. 
Already each MHC molecule can only bind a
subset of all possible polypeptides.
The classification of HLAs is based on algorithms that
maximize the information content of each 
classification, such as the presence of a certain amino acid at 
the first (for MHC-II, \cite{southwood1998several})
or second position (for MHC-I, \cite{lund2004definition}) of a polypeptide.
However, this does not imply that all polypeptides for a classification
pattern bind to the MHC, as there is no simple method to predict which 
MHCs bind which epitopes.
Using artificial neural networks, it became
possible to make theoretical predictions \cite{nielsen2003reliable,nielsen2004improved},
which are tested to be reliable in practice \cite{larsen2010identification,schellens2008unanticipated,tang2011genome}.

??? 
The polypeptides that can bind are also likelier to by hydrophobic,
as most TMHs have a hydrophobic binding pocket \richel{Reference needed}.
There are two sources of hydrophobic polypeptides, which are 
from membrane proteins and of soluble proteins.
Membrane proteins have at least one TMH to anchor them to
the membrane. TMHs are hydrophobic, as this is required to span the 
hydrophobic cellular lipid membrane. Additionally,
they often have a length of 23 amino acids to be able to span
the membrane.
Soluble proteins have (non-TMH) hydrophobic regions as well, 
to guides the protein to achieve its 3D configuration.

>>>>

Any human's immune system detects only a fraction of all possible
polypeptide fragments. 
Already each MHC molecule can only bind a
subset of all possible polypeptides (but it has been observed that HLA-A and HLA-B have no overlap in which
peptides they bind, \cite{lund2004definition}).
The classification of HLAs is based on algorithms that
maximize the information content of each 
classification, such as the presence of a certain amino acid at 
the first (for MHC-II, \cite{southwood1998several})
or second position (for MHC-I, \cite{lund2004definition}) of a polypeptide.
However, this does not imply that all polypeptides for a classification
pattern bind to the MHC, as there is no simple method to predict which 
MHCs bind which epitopes.
Using artificial neural networks, it became
possible to make theoretical predictions \cite{nielsen2003reliable,nielsen2004improved},
which are tested to be reliable in practice \cite{larsen2010identification,schellens2008unanticipated,tang2011genome}.

\richel{This is nonsense: 'The polypeptides that can bind are also 
likelier to by hydrophobic,
as most TMHs have a hydrophobic binding pocket': \cite{lund2004definition}
uses the hydrophobicity of some peptides for classification, but this
does not mean the statement is true}
There are two sources of hydrophobic polypeptides, which are 
from membrane proteins and of soluble proteins.
Membrane proteins have at least one TMH to anchor them to
the membrane. TMHs are hydrophobic, as this is required to span the 
hydrophobic cellular lipid membrane. Additionally,
they often have a length of 23 amino acids to be able to span
the membrane.
Soluble proteins have (non-TMH) hydrophobic regions as well, 
to guides the protein to achieve its 3D configuration.
